Reproducible research: A tutorial about doing the same thing more than once in R

### 2021-08-04 manuscript.Rmd
should have been bold

1. *Version control*
2. *Dynamic document generation*
3. *Dependency tracking*
4. *Software management*

@@

Defining the research questions and planning data analysis before observing the research outcomes is referred to as *preregistration* [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a-priori planned and theory-driven analyses from those conducted unplanned and post-hoc, that is, after having seen the data.
Preregistration seeks to reduce "researcher degrees of freedom" [@reference] in the execution of a planned study by limiting the number of decisions to be made after data has been collected, which could influence the results.
Preregistrations, however, have several shortcomings.
One shortcoming is that written study plans are often multi-interpretable and often do not achieve the level of unambiguity that are required to effectively zero the researcher degrees of freedom.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration are comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
These templates seek to improve the specificity of study plans by imposing structure [@bakkerEnsuringQualitySpecificity2020].
However, templates cannot remove researchers degrees of freedoms completely, because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.
A second limitation is that, just like primary research, preregistrations are susceptible to non-reproducibility.
To illustrate, a review of 210 preregistrations found that, even though 174 (67%) included a formal power analysis, only 34 (20%) of these could be reproduced [@bakkerRecommendationsPreregistrationsInternal2020].
Even when researchers have gone to great length in preregistering an analysis script,
they sometimes inexplicably fail to reproduce their own results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code results in different test statistic than they reported initially (see Footnote 7).
A final limitation is that written plans may turn out to be unfeasible once data are obtained and analyzed.
For example, a verbal description of a statistical model may be unidentified, e.g. if it includes reciprocal paths between variables, or more parameters than observed data.
Conversely, a model may be mis-specified in a major way; for example by omitting direct effects when the research question is about mediation, thus leading to a model with unacceptable fit.
Many researchers would only realize that such a model cannot be estimated once the data are obtained, thus necessitating a deviation from the preregistered plans.

@@

```{r}
simulate_data <- function(n, effect_size){
  # 1. warn users that the results are "fake"
  # 2. draw `n` samples with `effect_size`
  # 3. format and return in expected data format
}
```

>>>>

1. **Version control**
2. **Dynamic document generation**
3. **Dependency tracking**
4. **Software management**

@@

Defining the research questions and planning data analysis before observing the research outcomes is referred to as *preregistration* [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a-priori planned and theory-driven analyses from those conducted unplanned and post-hoc, that is, after having seen the data.
Preregistration seeks to reduce "researcher degrees of freedom" [@NosekRevolution2018] in the execution of a planned study by limiting the number of decisions to be made after data has been collected, which could influence the results.
Preregistrations, however, have several shortcomings.
One shortcoming is that written study plans are often multi-interpretable and often do not achieve the level of unambiguity that are required to effectively zero the researcher degrees of freedom.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis, the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration are comprehensive and specific enough is to use preregistration templates [like @bowmanOSFPreregTemplate2020].
These templates seek to improve the specificity of study plans by imposing structure [@bakkerEnsuringQualitySpecificity2020].
However, templates cannot remove researchers degrees of freedoms completely, because it is impossible to verbally describe every detail of an analysis for all but the most straightforward analysis.
A second limitation is that, just like primary research, preregistrations are susceptible to non-reproducibility.
To illustrate, a review of 210 preregistrations found that, even though 174 (67%) included a formal power analysis, only 34 (20%) of these could be reproduced [@bakkerRecommendationsPreregistrationsInternal2020].
Even when researchers have gone to great length in preregistering an analysis script,
they sometimes inexplicably fail to reproduce their own results.
For example, @steegenMeasuringCrowdAgain2014 realized after publication that part of their preregistered code results in different test statistic than they reported initially (see Footnote 7).
A final limitation is that written plans may turn out to be unfeasible once data are obtained and analyzed.
For example, a verbal description of a statistical model may be unidentified, e.g. if it includes reciprocal paths between variables, or more parameters than observed data.
Conversely, a model may be mis-specified in a major way; for example by omitting direct effects when the research question is about mediation, thus leading to a model with unacceptable fit.
Many researchers would only realize that such a model cannot be estimated once the data are obtained, thus necessitating a deviation from the preregistered plans.

@@

```{r, eval=FALSE}
simulate_data <- function(n, effect_size){
  # 1. warn users that the results are "fake"
  # 2. draw `n` samples with `effect_size`
  # 3. format and return in expected data format
}
```
